---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
library(tidyr)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(repos = list(CRAN="http://cran.rstudio.com/"))
```

# shinymetrics

<!-- badges: start -->
<!-- badges: end -->

The goal of shinymetrics is to produce metrics and accompanying plots for the shiny application on the FIND shinyapps.io server

## Installation

You can install the development version of shinymetrics like so:

``` {r}
install.packages("remotes")
remotes::install_github("finddx/shinymetrics")
```

## Example

This is a basic example which shows you how to retrieve number of connections per week for the FIND Sars-CoV-2 Test tracker application, from 01/09/2022 to 31/12/2022:

```{r example}
library(shinymetrics)
## basic example code
rsconnect::setAccountInfo(name='finddx',
			  token=Sys.getenv("SHINYAPPS_TOKEN"),
			  secret=Sys.getenv("SHINYAPPS_SECRET"))


apps <- rsconnect::applications(account = "finddx") 
app <- c("FINDCov19Tracker")
app_name <- c("FIND Sars-CoV-2 Test tracker")
server <- rep("shinyapps.io", length(app))
from <- rep("2022-09-01 0:00:00", length(app))
until <- rep("2022-12-31 0:00:00", length(app))

metrics_df <- metrics(app = app, app_name = app_name, 
                                    server = server, from = from, until = until)

unique(metrics_df$value)
p <- plot_metrics(df = metrics_df, weekly = TRUE, app_name = "FIND Sars-CoV-2 Test tracker")
print(p)
```


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
